Model LF

### 2022-10-31 Estimation.Rmd
Commit

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1) + L(log(mean_dp_regul),1) + d_2007q4)

>>>>

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1) + L(log(mean_dp_regul),1) + d_2007q4)

### Prod 1

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),1:4) +  L(TSDELTALOG(wage_ds),0:4)+  L(TSDELTALOG(mean_dp_regul),0:4) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(wage_ds),1)+ L(log(mean_dp_regul),1))

 prod_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 1:4)", c(1,3))
 wage_ds_vars_1 <- str_c("L(TSDELTALOG(wage_ds), 0:4)", c(1:4))
 dp_person_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(1:4))
  y_ds_vars_1 <- str_c("L(TSDELTALOG(y_ds), 0:4)", c(1:4))

vars_out_1 <- c( prod_vars_1, wage_ds_vars_1,dp_person_vars_1 ,y_ds_vars_1)
vars_out_1

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(prod_ds),c(4)) +  L(TSDELTALOG(wage_ds),0) +  L(TSDELTALOG(y_ds),0) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(wage_ds),1)+ L(log(mean_dp_regul),1))

### 2022-10-31 prod test.Rmd
Commit

@@

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low > 0

@@

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds =  prod - (alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3) + mean_prod
IF> shock_prod_model > 0

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$shock_lf_model = shock_lf_model

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds

tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
```

@@

```{r}
plot((emp_03-emp_bs3)*1000, col= "red")
```

>>>>

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) =  pr_1* TSDELTALOG(y_ds) + pr_2* TSDELTALOG(TSLAG(y_ds,1)) + pr_3* TSDELTALOG(TSLAG(prod_ds_shock,1)) + pr_4* TSDELTALOG(TSLAG(prod_ds_shock,4))+ pr_5* LOG(TSLAG(y_ds,1))  + pr_8* LOG(TSLAG(dp_person,1)) + pr_9* TSLAG(s_h,1) + pr_10* LOG(TSLAG(prod_ds_shock,1))
COEFF> pr_1 pr_2 pr_3 pr_4 pr_5 pr_8 pr_9 pr_10
STORE> coe(222)

@@

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
IF> shock_prod_model <= 0
IDENTITY> prod
EQ> prod=prod_ds + alpha_150 + SD1* alpha_151 + SD2*alpha_152 + SD3*alpha_153 - mean_prod
IF> shock_prod_model > 0

@@

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds = prod_ds_shock*1
IF> shock_prod_model > 0

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
   prod_ds_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$prod_ds_shock = prod_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
unemp_bs3 = Shock_bs3$simulation$unemp
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
```

@@

```{r}
plot((unemp_03-unemp_bs3)*1000, col= "red")
```
